Fully Automatic Loop-free Program Synthesis by Bounded Model Checking

### 2013-10-11 paper/paper.tex
Nudges

We do not compare {\sc Kalashnikov} to {\sc Sketch}~\cite{sketch}, since the problem domains are
too different to make a meaningful comparison.

The results of our experiments are shown in Fig.~\ref{fig:results-table} and Fig.~\ref{fig:icse-results-table}.
The results include the runtime for each tool, the number of lines in the synthesised program and whether
{\sc Brahma} was able to complete the synthesis completely automatically (the Aut. column).  A blank
in the Aut. column means that {\sc Brahma} was able to synthesise the program automatically, and a \xmark
means that user assistance was required.
On both sets of benchmarks, the results can be broadly divided into three categories:

>>>>

We do not compare {\sc Kalashnikov} to {\sc Sketch}~\cite{sketch}, since the problem domains are
too dissimilar to make a meaningful comparison.

The results of our experiments are shown in Fig.~\ref{fig:results-table} and Fig.~\ref{fig:icse-results-table}.
The results include the runtime for each tool, the number of lines in the synthesised program and whether
{\sc Brahma} was able to complete the synthesis completely automatically (the Aut. column).  A blank
in the Aut. column means that {\sc Brahma} was able to synthesise the program automatically, and a \xmark
\,means that user assistance was required.
On both sets of benchmarks, the results can be broadly divided into three categories:
